### 2019-12-23 thesis/mini/acknowledgments.tex
marting feedback 1

\vspace{1cm}
\noindent
I would like to thank Moritz for his great support, detailed feedback and his invaluable teaching how to do proper research.
I could not have imagined a better advisor for my master's thesis.

\noindent
Furthermore, I would like to thank Annibale for his helpful feedback and teaching me which is the proper vocabulary to describe my work.

\noindent
I want to pay my special regards to Prof. Pretschner for his critical questions, leading me to continuously challenge my evaluation and the problems my work addresses.

@@

\noindent
Lastly, I want to thank Michi and Taico.
Thank you for your calming input, critical reflection, your relentless support and upcheering.

>>>>

\vspace{1cm}
\noindent
I would like to thank Dr. Moritz Beller for his great support, his detailed feedback and his invaluable teaching how to do research.
I could not have imagined a better advisor for my master's thesis.

\noindent
Furthermore, I would like to thank Prof. Annibale Panichella for his helpful feedback and teaching me the proper vocabulary to describe my work.

\noindent
I want to pay my special regards to Prof. Alexander Pretschner for his critical questions, leading me to continuously challenge my evaluation and the problems my work addresses.
I would like to thank Prof. Alexander Knapp for his sharp eyes for formulas and our reassuring conversations.

@@

\noindent
Lastly, I want to thank Michi and Taico.
Thank you for your calming input, your critical reflection, your relentless support and  your upcheering.

### 2019-12-23 thesis/txt/0-introduction.tex
marting feedback 1

\chapter{Introduction}
Continuous Integration (CI) has become a common practice in software engineering~\cite{hilton2016usage}.
Many software projects use CI~\cite{hilton2016usage,staahl2014modeling,beller2017oops} to detect bugs early~\cite{vasilescu2015quality,duvall2007continuous}, improve developer productivity~\cite{miller2008hundred,hilton2016usage} and communication~\cite{downs2012ambient}.
A build on a CI server typically compiles and packages the software, executes tests~\cite{beller2017oops} and various kinds of static analyses~\cite{zampetti2017open}.

CI builds produce logs which report the results of the steps within the build.
These build logs contain a lot of valuable information for developers and researchers.
Developers examine log statements of time measurements to track how different stages of the build process perform.
Researchers collect the commands triggering the build steps to reverse engineer the build configuration when only the log is available to them.
Both groups analyze build logs for descriptions of compiler errors, linter warnings or failed tests to uncover why a CI build failed~\cite{beller2017oops,seo2014programmers,vassallo2017a-tale}.

The problem is, that build logs are verbose and long~\cite{beller2017oops}, making them inadequate for direct consumption.
Therefore, developers and researchers can only efficiently use the information within the build logs if they can adequately retrieve the parts (chunks) of the log that describe the targeted information.

% CI builds produce long and verbose build logs~\cite{beller2017oops}, reporting the progress and results of the steps within the build.
% The structure of these logs changes from project to project~\cite{staahl2014modeling} as it depends on the tools and the environment used.
% Build logs are a valuable data source for developers and researchers.
% Developers read them to analyze why their build failed or how different stages of the build process perform.
% Researchers can harvest the information contained in the logs to study the software engineering process of a project~\cite{rausch2017empirical,beller2017oops,seo2014programmers,vassallo2017a-tale}.
% However, these two groups can only use the information within the build logs if they can adequately retrieve the information relevant to them.

There are different techniques to retrieve information chunks from CI build logs.
Beller et al.\ use regular expressions to analyze the reasons of build failures from Travis CI logs~\cite{beller2017oops}.
Such regular expressions are developed by looking at a few exemplary build logs. Updating them whenever new cases are introduced is a tedious and error-prone task~\cite{michael2019regexes}.
Vassallo et al.\ wrote a custom parser for build logs to gather information for build repair hints~\cite{vassallo2018un-break}.
Recently, Amar et al.\ reduced the number of build log lines for a developer to inspect by creating a diff between the logs from a failed and a successful build~\cite{amar2019mining}.

These approaches have various strengths and weaknesses:
Regular expressions are exact but difficult to maintain~\cite{michael2019regexes}.
Custom parsers are powerful though fragile towards changes in the log structure.
The structure of build logs changes from project to project~\cite{staahl2014modeling} as it depends on the tools and the environment used.
Taking a diff between failed and successful logs can reduce the information to be processed, but the imprecise output needs to be interpreted by a developer~\cite{amar2019mining}.
At the moment there is only anecdotal evidence on the performance of these techniques and when a technique should be preferred over other alternatives.
Developers and researches currently have little support while choosing which technique to use for a task.

The goal of this thesis is to investigate different chunk retrieval techniques for build logs and describe under which circumstances each techniques is recommended over another.
We aim to characterize different chunk retrieval techniques, as well as the information retrievable from CI build logs.
For \textbf{RQ1}, we analyze which criteria influence the suitability of a chunk retrieval technique for CI build logs.
We implement and evaluate three chunk retrieval techniques:
\begin{itemize}
  \item program synthesis by example using the Microsoft PROSE library (referred to as PBE),
  \item a common text similarity approach (referred to as CTS), and
  \item keyword search (referred to as KWS).
\end{itemize}
\textbf{RQ2} asks under which conditions PBE, CTS and KWS are suited to retrieve information from continuous integration build logs.
\textbf{RQ2} is refined into sub-questions along with the criteria resulting from \textbf{RQ1} and compares their instantiations for the three techniques:
How many training examples a technique needs to perform best (\textbf{RQ2.1}), how structurally diverse the examples can be (\textbf{RQ2.2}) and how accurate the retrieved output is(\textbf{RQ2.3}).
To evaluate PBE, CTS and KWS we create a data set, namely \emph{LogChunks}, which encompasses about 800 log files from 80 repositories.
Each log is labeled with the log part describing the reason a build failed, keywords to search for this log part and a categorization of the labeled log part according to its structural representation within the log.

Our study of the three techniques on \emph{LogChunks} shows that
\begin{itemize}
  \item PBE yields very accurate results when trained with two examples from a single structural category.
  \item CTS shows the best average precision, though precision and recall of a retrieval is hard to determine from the given result.
  A small increase in the number of training examples has no noticeable influence.
  Fewer structural categories improve precision and recall of the retrieval.
  \item KWS has the highest recall of all techniques, however much lower precision.
  It is the technique with the best recall when multiple structural categories are present in the training examples.
\end{itemize}
We recommend PBE for use cases where the desired information is always represented in the same structural way and high confidence in precision and recall of the chunk retrieval is required.
CTS is well suited when the representation of the desired information varies slightly and the output of the chunk retrieval is further processed by a human.
In cases where the textual representation of the desired information in the log is unpredictable or varies greatly, KWS is the best technique to choose.
However, its low precision requires a human to interpret the output of the chunk retrieval.

@@

This thesis first presents an overview of related research, spanning from CI, build log analysis and augmentation to system log processing.
Chapter~\ref{sec:rw} also presents existing work on information extraction and retrieval techniques, as well as program synthesis from examples.
Next, Chapter~\ref{sec:techniques} characterizes chunk retrieval techniques and retrievable information from CI build logs.
It also introduces the three investigated techniques PBE, CTS and KWS\@.
Chapter~\ref{sec:data-set} describes the creation of the \emph{LogChunks} data set collected from failed Travis CI build logs, including the labeling and the validation process.
%Chapter~\ref{sec:implementation} outlines our implementation of the three chosen chunk retrieval techniques and the usage of our unified chunk retrieval tool.
This tool is also used for the comparison described in Chapter~\ref{sec:study}.
Chapter~\ref{sec:discussion} discusses the implications of the study results and recommendations on when PBE, CTS and KWS are most suitable.
Lastly, we conclude and give an overview of further research opportunities in Chapter~\ref{sec:conclusion-fw}.%\\\\

>>>>

\chapter{Introduction}
Continuous Integration (CI) has become a common practice in software engineering~\cite{hilton2016usage}.
Many software projects use CI~\cite{hilton2016usage,staahl2014modeling,beller2017oops} to detect defects early~\cite{vasilescu2015quality,duvall2007continuous}, improve developer productivity~\cite{miller2008hundred,hilton2016usage} and communication~\cite{downs2012ambient}.
A build on a CI server typically compiles and packages the software, executes tests~\cite{beller2017oops} and performs various kinds of static analyses~\cite{zampetti2017open}.

CI builds produce logs which report the results of the steps within the build.
These build logs contain valuable information for developers and researchers.
Developers examine log statements of time measurements to track how steps of the build process perform.
Researchers collect the commands triggering different build steps to reverse engineer the build configuration when only the log is available to them.
Both groups analyze build logs for descriptions of compiler errors, linter warnings or failed tests to uncover why a CI build failed~\cite{beller2017oops,seo2014programmers,vassallo2017a-tale}.

The problem is, that build logs are verbose and long~\cite{beller2017oops}, making them inadequate for direct consumption.
Therefore, developers and researchers can only efficiently use the information within build logs if they can adequately retrieve those parts (chunks) of the log that describe the targeted information.

There are different techniques to retrieve information chunks from CI build logs.
Beller et al.\ use regular expressions to analyze the reasons of build failures from Travis CI logs~\cite{beller2017oops}.
Vassallo et al.\ wrote a custom parser for build logs to gather information for build repair hints~\cite{vassallo2018un-break}.
Recently, Amar et al.\ reduced the number of build log lines for a developer to inspect by creating a diff between the logs from a failed and a successful build~\cite{amar2019mining}.

These approaches have various strengths and weaknesses:
Regular expressions are exact but difficult to maintain.
They are developed by looking at a few exemplary build logs. Updating them whenever new cases are introduced is a tedious and error-prone task~\cite{michael2019regexes}.
Custom parsers are powerful though fragile towards changes in the log structure.
The structure of build logs changes from project to project~\cite{staahl2014modeling} as it depends on the tools and the environment used.
Taking a diff between the logs of failed and successful builds can reduce the information to be processed, but the imprecise output needs to be interpreted by a developer~\cite{amar2019mining}.

At the moment there is only anecdotal evidence on the performance of these techniques and on when a technique should be preferred over other alternatives.
Developers and researches currently have little support when choosing which technique to use for a task.

The goal of this thesis is to investigate different chunk retrieval techniques for build logs and describe under which circumstances certain techniques can be recommended over others.
We aim to characterize different chunk retrieval techniques, as well as the information retrievable from CI build logs.
For \textbf{Research Question 1} (\textbf{RQ1}), we analyze which criteria influence the suitability of a chunk retrieval technique for CI build logs.
We implement and evaluate three chunk retrieval techniques:
\begin{itemize}
  \item program synthesis by example using the Microsoft PROSE library (referred to as PBE),
  \item a common text similarity approach (referred to as CTS), and
  \item keyword search (referred to as KWS).
\end{itemize}
\textbf{RQ2} asks under which conditions PBE, CTS and KWS are suited to retrieve information from continuous integration build logs.
\textbf{RQ2} is refined into sub-questions along with the criteria resulting from \textbf{RQ1} and compares their instantiations for the three techniques:
how many training examples a technique needs to perform best (\textbf{RQ2.1}), how structurally diverse the examples can be (\textbf{RQ2.2}) and how accurate the retrieved output is (\textbf{RQ2.3}).
To evaluate PBE, CTS and KWS we create a data set, called \emph{LogChunks}, which encompasses about 800 log files from 80 repositories.
Each log is labeled with the log part describing the reason a build failed, keywords to search for this log part and a categorization of the labeled log part according to its structural representation within the log.

Our study of the three techniques on \emph{LogChunks} shows that
\begin{itemize}
  \item PBE yields very accurate results when trained with two examples from a single structural category.
  \item CTS shows the best average precision, though precision and recall of a retrieval is hard to determine from the given result.
  A small increase in the number of training examples has no noticeable influence.
  Fewer structural categories improve precision and recall of the retrieval.
  \item KWS has the highest recall of all techniques, however much lower precision.
  It is the technique with the best recall when multiple structural categories are present in the training examples.
\end{itemize}

We recommend PBE for use cases where the desired information is always represented in the same structural way and high confidence in precision and recall of the chunk retrieval is required.
CTS is well suited when the representation of the desired information varies slightly and the output of the chunk retrieval is further processed by a human.
In cases where the textual representation of the desired information in the log is unpredictable or varies greatly, KWS is the best technique to choose.
However, its low precision requires a human to interpret the output of the chunk retrieval.

@@

This thesis first presents an overview of related research, spanning from CI, build log analysis and augmentation to system log processing.
Chapter~\ref{sec:rw} also presents existing work on information extraction and retrieval techniques, as well as program synthesis from examples.
Next, Chapter~\ref{sec:techniques} characterizes chunk retrieval techniques and retrievable information from CI build logs.
It also introduces the three investigated techniques PBE, CTS and KWS\@.
Chapter~\ref{sec:data-set} describes the creation of the \emph{LogChunks} data set collected from failed Travis CI build logs, including the labeling and the validation process.
%Chapter~\ref{sec:implementation} outlines our implementation of the three chosen chunk retrieval techniques and the usage of our unified chunk retrieval tool.
Chapter~\ref{sec:study} explains the empirical comparison of the three techniques on \emph{LogChunks} and presents the study results.
Chapter~\ref{sec:discussion} discusses the implications of the study results and recommendations on when PBE, CTS and KWS are most suitable.
Lastly,Chapter~\ref{sec:conclusion-fw} concludes and gives an overview of further research opportunities.%\\\\

### 2019-12-23 thesis/txt/1-related-work.tex
marting feedback 1

\section{Continuous Integration and Build Logs}
We describe existing studies about CI to show that CI is a relevant topic within the software engineering research community.
We explain how the researchers gather information about CI usage in software projects through build log analysis and why the chunk retrieval techniques we investigate simplifies their data collection.
Next, this section moves on to past works about augmenting build logs to make it easier for developers to inspect them.
The presented approaches are related to and can benefit from the techniques we analyze in this thesis.
Further, we classify build logs as semi-structured data and differentiate our work from system log analysis.
% CI describes the practice of integrating, building and testing source code changes often and fast.
% The tools involved in a CI build communicate their progress and status through a combined build log.
% In Section~\ref{sec:bl-characteristics}, we describe CI builds and how

@@

\subsection{Continuous Integration}
\label{sec:rw-ci}
The first paragraphs of this section present the results of past research into CI: its influence on the software engineering processes, the reasons for CI builds to fail and the role of testing and static analysis in CI builds.
Later we describe how these researchers obtain the data sets these works are based on.
We show how they analyze build logs and why the chunk retrieval techniques we investigate can support them to broaden their studies.
% This section starts with an overview on research into why CI is used and its impact on development.
% It presents analyses on why CI builds fail and how testing and static analysis tools are used within CI\@.
% We explain how researchers compose data sets for their work on CI and how chunk retrieval techniques can support them.

\paragraph{Motivation for CI and Impact of CI}
Why teams choose to use CI and its impac on the software development process is explored by several existing works.
Hilton et al.~\cite{hilton2017trade-offs} investigate the motivations of developers to use CI through several surveys.
Developers use CI to ensure consistency and quality across different execution environments and increase confidence into the code they deploy.
Hilton et al.~\cite{hilton2016usage} also analyze how and why open source projects use CI\@.
They observe CI usage in a broad range of projects, it supports them to catch bugs earlier and have more confidence in a successful build and shorten release cycles.
Stahl and Bosch~\cite{staahl2014modeling} provide a holistic review of literature on automatic build environments in industry projects.
They propose a descriptive structure to model build flows, which they found to be highly different from project to project.
Vasilescu et al.~\cite{vasilescu2015quality} analyze a broad rage of open source projects written in popular languages on GitHub.
They compare their usage of CI with the successful merges of pull requests and find that CI increase the number of successful merges, internal as well as external contributions, and allows the team members to uncover more bugs.
In a recent study, Vasallo et al.~\cite{vassallo2019every} interview developers on how they determine why a CI build failed.
They model how these developers resolve failures.
The first and most important steps when developers want to fix a build failure is to locate the error within the build log.
Then the developers use the additional information provided with and around the error message to understand the details of the failures.
This shows that the build log is a central source of information about a CI build.
% Vassallo et al.~\cite{vassallo2018continuous} conducted a survey study on how ci influences developers to continuously refactor their code to fix ci quality analysis warnings.
% Their results indicate that refactoring is rather spread in the ci environment and deemed important by the surveyed developers.
% ``Lack of time'' and ``absence of a proper test suite'' are named as the main barriers to continuous refactoring.
% Vassallo et al.~\cite{vassallo2019automated} analyzed build logs, source code repository content and build metadata of open source repositories for CI anti-patterns.

\paragraph{Build Failures in CI}
Various researchers look into why CI builds fail and the impact of build failures on the development workflow.
Seo et al.~\cite{seo2014programmers} find that a small group of error types such as dependency mismatches are the most prominent cause of build failures at Google.
In addition, most failures are resolved within two builds.
Rausch et al.~\cite{rausch2017empirical} analyze CI builds of open source Java projects and categorize why builds failed.
Most builds fail because of failing tests.
For most projects, over half of the failed builds follow another failed build.
Their data shows that most failures occur in the second half of the build runtime, which can cause long delays in the feedback loop, especially when builds are automatically retried upon failure.
Vassallo et al.~\cite{vassallo2017a-tale} compare open source projects in Java to industrial ones.
They determine that testing failures are more common than compilation errors.
Open source builds fail most often because of unit tests, whereas release preparations is the primary cause in industrial projects.

\paragraph{Static Analysis and Testing in CI}
Automated static analysis tools are the focus of Zampetti et al.~\cite{zampetti2017open} in their study of java projects from GitHub.
Their results show that static analysis is responsible for a small amount of build failures and mainly responsible for warned builds.
Almost all analyzed projects use custom configurations for the static analysis, however the configuration rarely changes.
Failures because of static analysis warnings are fixed in a short time frame.
Beller et al.~\cite{beller2017oops} show that testing is central to continuous integration when evaluating Travis CI logs for Java and ruby builds.
They observe a high variety between programming langues, i.e. in the kind and number of tests which are run, as well as how often tests fail.
The low failure rates on the CI server hint at code being tested before it is sent to the server.

\paragraph{Data Sets Powering CI Research}
The works presented in this section are based on either developer surveys or data sets, containing build metadata or build logs.
Seo et al.~\cite{seo2014programmers} and Vassallo et al.~\cite{vassallo2017a-tale} based their analyses on sets of build logs collected from industry partners.
Beller et al.~\cite{beller2017travistorrent} created the \emph{TravisTorrent} data set providing access to build metadata from more than 1,000 projects from Travis CI~\cite{travisci2019webpage}.
TravisTorrent was the basis for several of the works mentioned in this section~\cite{rausch2017empirical,zampetti2017open,vassallo2017a-tale,beller2017oops}.
Ghaleb et al.~\cite{ghaleb2019studying} aim to identify noise in build breakage data.
They classify build failures from \emph{TravisTorrent} according to whether they were caused by an environmental failure or caused by a developer change.
They also identify cascading build failures created by existing unfixed errors and allowed failures, whose results were later labeled by developers to be ignored.
About half of the failed builds in \emph{TravisTorrent} fall into at least one of these categories.
When regarded as noise they considerably impact observations reported by other works modeling build breakages.

>>>>

\section{Continuous Integration and Build Logs}
We describe existing studies about CI to show that CI is a relevant topic within the software engineering research community.
We explain how researchers gather information about CI usage in software projects through build log analysis and why the chunk retrieval techniques we investigate simplifys their data collection.
This section moves on to past works about augmenting build logs to make it easier for developers to inspect them.
The presented approaches are related to and can benefit from the techniques we analyze in this thesis.
Further, we classify build logs as semi-structured data and differentiate our work from system log analysis.
% CI describes the practice of integrating, building and testing source code changes often and fast.
% The tools involved in a CI build communicate their progress and status through a combined build log.
% In Section~\ref{sec:bl-characteristics}, we describe CI builds and how

@@

\subsection{Continuous Integration}
\label{sec:rw-ci}
The first paragraphs of this section present the results of past research into CI: its influence on the software engineering processes, the reasons for CI builds to fail and the role of testing and of static analysis in CI builds.
Later we describe how researchers obtain the data sets these works are based on.
We show how they analyze build logs and why the chunk retrieval techniques we investigate can support them to broaden their studies.
% This section starts with an overview on research into why CI is used and its impact on development.
% It presents analyses on why CI builds fail and how testing and static analysis tools are used within CI\@.
% We explain how researchers compose data sets for their work on CI and how chunk retrieval techniques can support them.

\paragraph{Motivation for CI and Impact of CI}
Why teams choose to use CI and its impact on the software development process is explored by several existing works.
Hilton et al.~\cite{hilton2017trade-offs} investigate the motivations of developers to use CI through several surveys.
They find that, developers use CI to ensure consistency and quality across different execution environments and increase confidence in the code they deploy.
Hilton et al.~\cite{hilton2016usage} also analyze how and why open source projects use CI\@.
They observe CI usage in a broad range of projects, it supports developers to catch bugs earlier and to shorten release cycles.
Stahl and Bosch~\cite{staahl2014modeling} provide a review of literature on automatic build environments in industry projects.
They propose a descriptive structure to model build flows, which they found to be highly different from project to project.
Vasilescu et al.~\cite{vasilescu2015quality} analyze a broad rage of open source projects written in popular languages on GitHub.
They compare the usage of CI with the successful merges of pull requests and find that CI increase the number of successful merges and allows the team members to uncover more bugs.
In a recent study, Vasallo et al.~\cite{vassallo2019every} interview developers on how they determine why a CI build failed and model how these developers resolve failures.
Vasallo et al. find that, the first and most important steps when developers want to fix a build failure is to locate the error within the build log.
Then the developers use the additional information provided with and around the error message to understand the details of the failures.
This shows that the build log is a central source of information about a CI build.
% Vassallo et al.~\cite{vassallo2018continuous} conducted a survey study on how ci influences developers to continuously refactor their code to fix ci quality analysis warnings.
% Their results indicate that refactoring is rather spread in the ci environment and deemed important by the surveyed developers.
% ``Lack of time'' and ``absence of a proper test suite'' are named as the main barriers to continuous refactoring.
% Vassallo et al.~\cite{vassallo2019automated} analyzed build logs, source code repository content and build metadata of open source repositories for CI anti-patterns.

\paragraph{Build Failures in CI}
Various researchers look into why CI builds fail and into the impact of build failures on the development workflow.
Seo et al.~\cite{seo2014programmers} find that a small group of error types such as dependency mismatches are the most prominent cause of build failures at Google.
In addition, they notice that most failures are resolved within two builds.
Rausch et al.~\cite{rausch2017empirical} analyze CI builds of open source Java projects and find that most builds fail because of failing tests.
For most projects, over half of the failed builds follow a previous failed build.
Rausch et al.'s data shows that most failures occur in the second half of the build runtime, which can cause long delays in the feedback loop, especially when builds are automatically retried upon failure.
Vassallo et al.~\cite{vassallo2017a-tale} compare open source projects in Java to industrial ones.
They determine that testing failures are more common than compilation errors.
Open source builds fail most often because of unit tests, whereas release preparations are the primary cause in industrial projects.

\paragraph{Static Analysis and Testing in CI}
Automated static analysis tools are the focus of Zampetti et al.~\cite{zampetti2017open} in their study of Java projects from GitHub.
Their results show that static analysis is responsible for a small amount of build failures and mainly responsible for warned builds.
Almost all analyzed projects use custom configurations for the static analysis, however the configuration rarely changes.
Failures because of static analysis warnings are observed to be fixed in a short time frame.
Beller et al.~\cite{beller2017oops} show that testing is central to continuous integration when evaluating Travis CI logs for Java and Ruby builds.
They observe a high variation between programming langues, in the kind and number of tests which are run, as well as how often tests fail.
The low failure rates on the CI server hint at code being tested before it is sent to the server.

\paragraph{Data Sets Powering CI Research}
The works presented in this section are based on either developer surveys or data setsa containing build metadata or build logs.
Seo et al.~\cite{seo2014programmers} and Vassallo et al.~\cite{vassallo2017a-tale} based their analyses on sets of build logs collected from industry partners.
Beller et al.~\cite{beller2017travistorrent} created the \emph{TravisTorrent} data set providing access to build metadata from more than 1,000 projects from Travis CI~\cite{travisci2019webpage}.
\emph{TravisTorrent} was the basis for several of the works mentioned in this section~\cite{rausch2017empirical,zampetti2017open,vassallo2017a-tale,beller2017oops}.
Ghaleb et al.~\cite{ghaleb2019studying} aim to identify noise in build breakage data.
They classify build failures from \emph{TravisTorrent} according to whether they were caused by an environmental failure or caused by a developer change.
They also identify cascading build failures created by existing unfixed errors and allowed failures, whose results were later labeled by developers to be ignored.
About half of the failed builds in \emph{TravisTorrent} fall into at least one of these categories.
When regarded as noise they considerably impact observations reported by other works modeling build breakages.
